Different rules for binocular combination of luminance flicker in cortical and subcortical pathways

### 2023-06-11 manuscript.Rmd
Add processed data files to a local zip file in the repository to avoid having to download from OSF

if (processdata>0){
if (!file.exists(paste0(datadir,'headerfile.csv'))){
# copy from resources folder
file.copy('resources/headerfile.csv',paste0(datadir,'headerfile.csv'))
}

if (!file.exists(paste0(localdir,'StimulusExample.png'))){
# copy from resources folder
file.copy('resources/StimulusExample.png',paste0(localdir,'StimulusExample.png'))
}
}

if (processdata==2){
# if we're going to need the pre-processed files, download all in a zip file
  if (!file.exists(paste0(datadir,'P101summary.RData'))){
          osfnode <- '2qu6y'
          osfproject <- osf_retrieve_node(osfnode)
          osffiles <- osf_ls_files(osfproject,n_max=300)
          fid <- which(osffiles$name=='allprocessed.zip')
          osf_download(osffiles[fid,],localdir,progress=TRUE)
          unzip(paste0(localdir,'allprocessed.zip'),exdir=localdir)
          d <- dir(paste0(localdir,'allprocessed'),full.names=TRUE)
          file.copy(d,datadir)
  }
}

@@

>>>>

if (processdata>0){
if (!file.exists(paste0(datadir,'headerfile.csv'))){
# copy from resources folder
file.copy('resources/headerfile.csv',paste0(datadir,'headerfile.csv'))
} 
if (!file.exists(paste0(localdir,'StimulusExample.png'))){
# copy from resources folder
file.copy('resources/StimulusExample.png',paste0(localdir,'StimulusExample.png'))
}
}

if (processdata==2){
# if we're going to need the pre-processed files, extract from zip file
  if (!file.exists(paste0(datadir,'P101summary.RData'))){
   if (file.exists('resources/allprocessed.zip')){file.copy('resources/allprocessed.zip',localdir)}
   if (!file.exists('resources/allprocessed.zip')){ 
          osfnode <- '2qu6y'
          osfproject <- osf_retrieve_node(osfnode)
          osffiles <- osf_ls_files(osfproject,n_max=300)
          fid <- which(osffiles$name=='allprocessed.zip')
          osf_download(osffiles[fid,],localdir,progress=TRUE)
   }
          unzip(paste0(localdir,'allprocessed.zip'),exdir=localdir)
          d <- dir(paste0(localdir,'allprocessed'),full.names=TRUE)
          file.copy(d,datadir)
  }
}

@@

Figures \@ref(fig:appendixfig1) and \@ref(fig:appendixfig2)

```{r appendixfig1, fig.cap="S.", fig.align="center", echo=FALSE}

knitr::include_graphics(paste0(figdir,'pupildataRep.pdf'))

```{r appendixfig2, fig.cap="S.", fig.align="center", echo=FALSE}

knitr::include_graphics(paste0(figdir,'EEGdataRep.pdf'))
